---
title: 'PSYC4960: Quiz 1'
author: "Amanda Mae Woodward"
date: "2/3/2022"
output: html_document
---
Assignment: For this assignment, you will need to use the skills you have developed in the last two weeks. You **are** allowed to work with each other, but answers are graded based on accuracies

**Pt 1**
1. Create a dataframe containing two columns: one with five super heroes, and one with your rating of how effective they are (1 = not effective; 10 = very effective)
```{r}
superHero<- c("Batman", "Superman", "WonderWoman", "BlackPanther", "Flash")
rating<- c(2,7,8,10,4)
superHeroDat<-cbind.data.frame(superHero, rating)
```

2. What are the mean and standard deviation of your ratings? 
```{r}
mean(superHeroDat$rating)
sd(superHeroDat$rating)
```
3. Print just the row containing your highest ranked hero.
```{r}
superHeroDat[4,]
```

4. Write a logical statement to determine if your highest ranked superhero and second highest ranked hero have the same ranking
```{r}
superHeroDat[4,]==superHeroDat[3,]
```
no they are not ranked the same 

**Part 2**
5. Create a function that indicates whether a number is above 50 or 50 or under
```{r}
underFifty<-function(thing){
  ifelse(thing>50, "greater than 50", "less than 50")
}
```

6. Test your function by inputting the number 19
```{r}
underFifty(19)
```

7. Create a vector containing the numbers 1 through 100.
```{r}
numbers<-1:100
```

8. Modify your function to test whether each number in the vector are even or odd. (hint: this means you need to iterate through a list!) 
```{r}
evenOdd<-function(number){
  ifelse(number%%2==0, "even","odd")
}
```

9. Test your new function using the vector in #6. 
```{r}
evenOdd(numbers)
```

**Pt 3**
All questions will use the diamonds dataset (in the ggplot2 library).
```{r}
library(ggplot2)
data(diamonds)
```
10. Summarize the dataset.
```{r}
summary(diamonds)
```

11. What type of variable is cut? How do you know? 
```{r}
class(diamonds$cut)
```
cut is an ordered factor b/c that's what the class function returned 

12. What type of variable is price? How do you know?
```{r}
class(diamonds$price)
```
price is an integer because that's what class() returned 
13. Create a subset of the dataset that contains all diamonds with a VS1 clarity. 
```{r}
vsdiamonds<-subset(diamonds,diamonds$clarity=="VS1")

```

14.How many diamonds are in this dataset? 
```{r}
nrow(vsdiamonds)
```
there are 8171 diamonds 

15. Add a column to this subset indicating whether a diamonds' carat is small (less than the first quartile), average (between the first and third quartile), or large (greater than the third quartile).
```{r}
vsdiamonds$caratSize<-NA
sumDiamonds<-summary(vsdiamonds$carat)
str(sumDiamonds)
for(i in 1:nrow(vsdiamonds)){
  if(vsdiamonds$carat[i]<.38){
    vsdiamonds$caratSize[i]<- "small"
  }
  if(vsdiamonds$carat[i]<1.01){
    vsdiamonds$caratSize[i]<- "large"
  }
  else{
    vsdiamonds$caratSize[i]<- "average"
    }
}
```

