---
title: "Dataset Manipulation Answers"
author: "Amanda Mae Woodward"
date: "3/28/2022"
output: html_document
---
1.Open the sleep dataset in R 
```{r}
data(sleep)
```

2. Is it long or wide format? How do you know? 
long format- each participant has data in 2 rows
3. Transform this data so that it is in the other format. 
```{r}
library(tidyverse)
colnames(sleep)
wideDat<-pivot_wider(sleep, id_cols="ID", names_from = "group", values_from="extra")
```

4. Transform your data back to its original format. 
```{r}
colnames(wideDat)
longDat<-pivot_longer(wideDat, cols=c('1','2'), names_to = "GroupNumber",values_to="extraSleep")
```

5. Open the Starwars dataset
```{r}
data(starwars)
```

6. Create homeworld as a factor. How many levels does it have? 
```{r}
starwars$homeworld<-as.factor(starwars$homeworld)
length(levels(starwars$homeworld))
```
48 levels
7. Reorder homeworld so that Naboo is the reference group. 
```{r}
starwars$homeworld2<-relevel(starwars$homeworld, ref="Naboo")
```

8. Use mutate to create a column transforming kg to pounds. (hint: you may need to look up the conversion)
```{r}
starwars2<-starwars %>% mutate(massLbs=mass*2.20) 
```

9. Print a summary of your column from #8
```{r}
summary(starwars2$massLbs)
```
