---
title: "Quiz 2 Answers"
author: "Amanda Mae Woodward"
date: "3/28/2022"
output: html_document
---
This quiz is meant to help you synthesize materials we've covered in class. If you'd prefer to use other functions, that's okay too. 

You ARE allowed to work with your peers, but you should each submit your own copy.

 You should see the following variables: 
subj- subject number
condition- experimental or control
stroop- an accuracy score for the stroop task (30 trials)
nback- an accuracy score for the n back task (recalling a number/object a given number of trials back;50 trials)
ravens- score on raven's progressive matrices (25 trials)

People are assigned to either complete a cognitive training task (to improve memory) or to have no training. We have  

Upload the psych259-Quiz2.csv file.
```{r}
dat<- read.csv("~/Desktop/PSY4960/PSY4960-Quiz2.csv")
```

1. Take a summary of the full dataset.
```{r}
summary(dat)
```

2. What kind of data do you have (wide or long?). How do you know?
data are in wide format because each participant has all responses in a single row (columns represent different variables measured at different time points)
3. Check the type of data presented in the condition column. Make sure this variable is a factor
```{r}
class(dat$condition)
dat$condition<-as.factor(dat$condition)
```

4. Create a new column called Stroop Accuracy.
Label those who have a higher than average score at t1 "high EF", those below average "low EF" and those at average "Average EF" (Note: EF stands for executive function). 
```{r}
dat$stroopAccuracy<-ifelse(dat$t1_stroop> mean(dat$t1_stroop), "High EF", ifelse(dat$t1_stroop==mean(dat$t1_stroop), "Average EF", "Low EF"))
```

5. Create a dataset containing participants' nback scores in long format. (Note: you should keep all other variables)
```{r}
library(tidyverse)
colnames(dat)
nBackLong<-pivot_longer(dat, cols=c("t1_nback", "t2_nback"), names_to = "timePoint",values_to = "nbackScore")
```
6. Returning to the original dataset, create a column indicating the difference between the two ravens scores. 
```{r}
dat$ravensDiff<-dat$t2_ravens-dat$t1_ravens
```

7. Based on #6, create two subsets of data: 1 where the ravens difference score is positive and one where it is negative
```{r}
posRavens<- subset(dat, dat$ravensDiff>0)
negRavens<- subset(dat, dat$ravensDiff<0)

```

