---
title: "PSY4960 Quiz 3"
author: "Amanda Mae Woodward"
date: "03/15/2022"
output: html_document
---
This quiz will require you to combine some of the information we've learned about making graphs.

1. Open the starwars dataset. 
```{r}
library(tidyverse)
data(starwars)
```

2. Create a summary table of character's heights based on their species.
```{r}
library(Rmisc)

speciesHeight<- summarySE(starwars, groupvars="species", measurevar = "height", na.rm=TRUE)
```

3. Use information from #2 to create a bar graph of the average height for each species. (add standard error bars to your graph and make sure to change at least two aesthetic elements of the graph)
```{r}
ggplot(speciesHeight, aes(species, height)) + geom_bar(stat="identity",fill= "#336699")+ geom_errorbar(aes(ymin= height - se, ymax= height +se))+theme_classic()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```

4. Create a graph of the Homeworld column. What is the most common homeworld? 
```{r}
ggplot(starwars, aes(homeworld))+geom_bar()+theme_classic()+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```
Naboo is the most common homeworld 

5. Create a subset for all characters who were in Return of the Jedi (Note: we haven't learned how to separate information in the film column- so you can just select the ones who were ONLY in Return of the Jedi)
```{r}
starwars2<- starwars %>% filter(films=="Return of the Jedi")
```

6. Using this subset of data, create a scatterplot of height versus weight.
```{r}
ggplot(starwars2, aes(height, mass))+geom_point()+theme_classic()
```

7. Add a regression line to the scatterplot you created in #6. 
```{r}
ggplot(starwars2, aes(height, mass))+geom_point()+theme_classic()+geom_smooth(method="lm")
```

8. Open the mtcars dataset. 
```{r}
data(mtcars)
```

9. Use facet_wrap to create a graph of the relationship between mpg and hp. Use cylinder to create facets
```{r}
ggplot(mtcars, aes(mpg,hp))+geom_point()+facet_wrap(~cyl)
```


10. Create a graph of hp and mpg. Add cyl as a third variable
```{r}
library(viridis)
ggplot(mtcars, aes(mpg,hp,color=as.factor(cyl)) )+geom_point()+theme_classic()+scale_color_viridis(discrete=TRUE, option="A")
```
