---
title: "PSY4960-basicfunctionsinRpt2"
author: "YOURNAMEHERE"
date: "2/2/2022"
output: html_document
---
1.create a variable that contains 8 tv show names.
```{r}
shows<- c("Grey's Anatomy", "New Girl", "It's Always Sunny", "Gilmore Girls", "Grace and Frankie", "Vampire Diaries", "That 70s Show", "Criminal Minds")
```

2. What kind of data is this? explain how you know.
Currently, this is character level.
```{r}
class(shows)
```
When I use the class function, it returns "character"

3. Change your variable to a factor. 
```{r}
shows<-as.factor(shows)
```

4. create a vector that contains your rating from 1 (hate it)-5 (love it) of the TV shows you named 
```{r}
ratings<- c(7,6,8,7,6,7,8,8)
```
5. Combine these two variables into a data frame
```{r}
dat<-cbind.data.frame(shows, ratings)
```

6. Add a column to your dataframe called "goodOrBad." fill in the variable with your opinion about each show
```{r}
dat$qualRating<- rep("good", nrow(dat))
```

7. Create a function that multiplies numbers by 13.
```{r}
mult13<- function(number){
  number*13
}
```

8. Create a dataframe that consists of one vector, which  contains the numbers 1-13
```{r}
numbers<-1:13
numberDat<-data.frame(numbers)
```

9. Test your function from #7 by creating a new column in your dataframe from #8 that contains the output from your function for the numbers 1-13  (i.e. use the column you already made to test your function)
```{r}
numberDat$multiplied<- mult13(numberDat$numbers)
```

10. Use a for loop to determine if the numbers in your column from #9 are even or odd (Hint: %% is a logical operator that tells you if there's a remainder.) 
```{r}
for(i in 1:length(numberDat$multiplied)){
  if(numberDat$multiplied[i]%%2==0){
    print("even")
  }
  else{print("odd")}
}
```

11. Challenge save this output to another column in your data frame. 
```{r}
numberDat$evenOdd<-NA
for(i in 1:length(numberDat$multiplied)){
  if(numberDat$multiplied[i]%%2==0){
    numberDat$evenOdd[i]<-"even"
  }
  else{numberDat$evenOdd[i]<-"odd"}
}
```

12. use if/else statements to create a column that indicates whether the numbers in the column created for #9 are "bigger" than 100 or "smaller" than 100.
```{r}
numberDat$big100<-ifelse(numberDat$multiplied>100, "bigger", "smaller")
```

